Lens Recovery with GLASS: An Extensible Free-Form Gravitational Lens Modeling Framework

### 2013-05-27 limits/ms.tex
New plots of sigma/beta and sample reconstruction. Beginnings of stellar mass and vel disp sections.

\documentclass[onecolumn,galley]{mn2e}
%\documentclass[onecolumn,galley,draft]{mn2e}
%\usepackage{myaasmacros}
\usepackage{mathrsfs}
\usepackage{amsmath}
\usepackage{graphicx}

@@

A typical lens, where only the measured observables are the image positions,
can been used to estimate the total mass of a galaxy including parts of the
dark matter halo. The enclosed mass inside the Einstein radius is simple to
calculate and quite robust given the observed image positions. The exact mass
distribution is more difficult to determine, however, as there are typically
not enough constraints of the mass profile. The known degeneracies have been
discussed at length in the literature. At the very least, one would like to
have a measure of the enclosed mass at at least two distinct radii to be able
to distinguish between analytic mass models. This would break the steepness
degeneracy, also known as the mass sheet degeneracy.

Other than using the Einstein radius, the enclosed mass can be estimated
from stellar velocity dispersions. If the radius from this measurement
is sufficiently different from the Einstein radius, then this provides the
necessary data. Another solution, is to find a galaxy that is lensing two
sources. The images from each source would provide an enclosed mass. The
extent to which the radii differ is dependent upon the redshifts of the
two sources: the larger the difference the larger the difference in radii.

If one assumes knowledge of the Hubble constant $H_0$ and time delays have been
observed for a lens. In principle, this determines that mass, but in practice
this can only place strong constraints on the mass distribution, as it does not
solve the problem that the exact distribution is highly degenerate. One can
choose to postpone this problem and simply fit models to the given data.  The
earliest examples were singular isothermal sphere (SIS) or elliptical (SIE)
models but have since evolved to multi-component models include separate models
for the stars and dark matter. Other methods that do not ignore this problem
use genetic algorithms or linear programming to explore the large space of
solutions.

Worse, though, is when only time delays are known and $H_0$ is to be inferred.
In this case, one is again free to change the mass and $H_0$ while keeping
all observables fixed. A single lens can say almost nothing about the actual
value of $H_0$. However, it has been shown that combining the modeling results
of several strong lenses with time delays can significantly reduce the allowed
values and provides a measure to within 10 percent.

Despite these difficulties lensing is a direct probe of the gravitating
mass in a halo and there are a number of open problems in galaxy formation
that lensing can help address. For instance, the debate remains as to what
form the inner slope of the density profile takes. Numerical simulations of
dark matter suggest a cusp, while observations from lensing and stellar dynamics
suggest cores. This may, however, be only a matter of scale, as both theory
and observations agree that clusters have cuspy profiles.

@@

\Glass\ is an evolution of the concepts employed by the free form modeling tool
\PixeLens\ but completely rewritten in Python and C. The key improvements are:
\begin{enumerate}
  \item A modular framework allows new priors to be added and modified easily.
  \item The basis functions approximating a model can be changed. 
  \item Non-linear constraints can be imposed in an automated post-processing step. 
  \item The central region can be have a higher resolution to capture steep models. 
  \item Stellar density can be used as an additional constraint.  
  \item Point or extended mass objects can be placed in the field.
\end{enumerate}
In our tests we will take advantage of each of these new features.  At its
heart lies a new algorithm for sampling high dimensional linear spaces that is
used to generate lensing models. This algorithm was described and tested in
\cite{}. \Glass\ is also multi-threaded allowing it to run efficiently on
many-cored machines.  The software is freely available for download. One
interesting aspect is that the input files are themselves Python programs. This
allows a large amount of sophistication in setting up a lens at runtime and
also allows \Glass\ to be used as an external library from another user written
program.

@@

For this paper we will restrict ourselves to using the pixelated basis set that
has been employed in previous work and is implemented in \PixeLens. Here we will
briefly review the main ideas. The algorithm for generating models in \Glass\
samples a convex polytope in a high dimensional space whose interior points are
solutions to the lensing equation and satisfy other physically motivated linear
priors. We must therefore formulate all of our equations as equations linear in the
unknowns. We describe the density distribution
$\kappa$ as a set of discrete grid cells or pixels $\kappa_i$.
In this way, we rewrite the potential (\eqnref{lensing potential}) as
%
\begin{equation}
  \psi(\vec\theta) = \sum_n \kappa_n Q_n(\vec\theta)
  \label{discrete potential}
\end{equation}
%
where the sum runs over all the pixels and $Q_n$ is the integral of the logarithm
over pixel $n$. The exact form for $Q$ is described in \appref{Q derivation}.
We can find the discretized lens equation by simply taking the gradient of the
above equations.

The pixels only cover a finite circular area with physical radius $\Rmap$ and 
pixel radius $\Rpix$. To account for any global shearing outside this region
from, e.g., a neighboring galaxy, we also add two shearing terms
%
\begin{equation}
\gamma_1(\theta_x^2 - \theta_y^2) + 2\gamma_2\theta_x\theta_y\quad.
\end{equation}
%
We can continue adding terms to account for assumed potentials or potentials
induced from the presence of other galaxy in the field. If the stellar density
has been estimated we can use this as a lower bound where the stellar potential
is a known constant of the form \eqnref{discrete potential}.
%
%\begin{equation}
  %\psi^*(\vec\theta) = \sum_n \kappa^*_n Q_n(\vec\theta)\quad.
%\end{equation}
%

Unfortunately, the lens equation and the arrival times are not enough to form a
closed volume in the solution space. We have not imposed any strong constraints
on the density even so much as to ensure that it is non-negative everywhere. We
must therefore provide additonal linear constraints so that we generate
physical models. The explicit implementation for these priors has been
explained in \cite{}. In summary, we require that
\begin{enumerate}
\item The density must be non-negative everywhere.
\item The density profile must have a slope everywhere $\le 0$. This prevents hollow rings.
\item The local gradient everywhere must point within $45^{\circ}$ of the center.
\item Density variations must be smooth.
\item Image parity is enforced.
\item The density is radially symmetric. (Optional)
\end{enumerate}

@@

\subsection{Raytracing}
\label{Raytracing}
\Glass\ can also determine the position of images and time delays from 
particle-based simulation output given a source position $\vec\beta$. This is
used to generate the lens configurations used in the parameter study.  The
particles are first projected onto a very high resolution grid representing the
lens plane. The centers of each of the grid cells are mapped back onto the
source plane using \eqnref{lensing equation}. If the location on the source
plane is within a user specified $\eps_\mathrm{accept}$ of $\vec\beta$ then the
point on the image plane is accepted and further refined using a root finding
algorithm until the distance to $\vec\beta$ is nearly zero. If multiple points
converge to an $\eps_\mathrm{root}$ of each other then only one point is taken.
Care must be taken that the grid resolution is high enough that the resulting
image position error is below the equivalent observational error. Time delays
are the calculated in order from the arrival time at each image (\eqnref{tau}).

@@

The four mock galaxies we consider have been designed to test our recovery
procedure on galaxies that have steep and shallow dark matter and stellar
profiles. The enclosed mass in all cases is fixed at $M(a_\star)= 0.18\e{11}$
at the scale radius $a_\star=2$ kpc. These values were chosen to closely
resemble B1115. We therefore place the galaxy at a redshift of $z_L = 0.31$.
Throughout, we assume a cosmology where $H_0^{-1}=13.7$ Gyr, $\Omega_M=0.28$,
and $\Omega_\Lambda=0.72$. The critical density is $\kappa_\mathrm{crit}\sim
1.8\e{9}$\Msun/kpc$^2$.

The models were
first generated as three dimensional particle distributions with the
tool DEHNEN, where each component follows the profile
\begin{equation}
\rho(r) = \frac{M}{4\pi a^3}(3-\gamma){(r/a)^{-\gamma}(1 + r/a)^{\gamma-4}}
\label{Dehnen profile}
\end{equation}
and where $\gamma$ is the profile index and $a$ is the scale radius. The
four combinations of profile indices are shown in \tabref{Lens profile params}.

\begin{table}
\begin{tabular}{cllllllll}
Galaxy & $\gamma_\star$ & $M_\star$ & $\gamma_\mathrm{DM}$ & $M_\mathrm{DM}$ & Notes\\
\hline
AA & 1 & 4 & 0.05 & $11^{2.95}$ & \\
AC & 1 & 4 & 1 & $11^2$ & \\
BB & 1.5 & $2^{1.5}$ & 0.16 & $11^{2.84}$ & \\
BC & 1.5 & $2^{1.5}$ & 1 & $11^2$ & 
\end{tabular}
\caption{Profile parameters for the four mock galaxies. The resulting profiles only roughly follow
\eqnref{Dehnen profile} because the galaxies are triaxial. Masses are in units of $0.18\e{11}\Msun$. The scale lengths for
all lenses are $(a_\star,a_\mathrm{DM})=(2,20)$ kpc and by definition
$M_\star(a_\star) = M_\mathrm{DM}(a_\star) = 1$.}
\label{Lens profile params}
\end{table}

@@

\begin{enumerate}
\item Two double imaged systems with a single point source.
\item Two quadruply imaged systems with a small and large annulus.
\item Two quadruply imaged systems with a single point source.
\item One extended source. 
\item A two-source quad system with one source varying across five redshifts. 
\end{enumerate}

Each of these configurations were modeled with and without time delays and with
and without a central image. We assumed for all tests that the lensing mass was
symmetric.

\subsection{Stellar mass}
\begin{itemize}
\item Assume perfect knowledge of the stellar mass distribution.
\item Construct a lens system where the images are probing the stellar region.
\item Add stellar mass as a minimum constraint on the pixels.
\item Requires more pixels in the middle to correctly and efficiently be resolved
\item Stellar mass improves the reconstruction. Need to explain how.
\end{itemize}

\subsection{Velocity dispersions}

\begin{itemize}
\item Can they predict radial profiles?
\item Can we constrain lensing models from predicted velocity dispersions?
\item Use a constructed spherical halo G2 following a $\rho \propto r^{-\gamma}$ profile with stellar halo same as G1.
\item Vary $z$ of the halo, possibly orientation.
\item Should be able to recover $\gamma$ very well.
\item Use G1. Show problems with recovering $\gamma$.
\end{itemize}

@@

%\begin{figure}
%\plotone{AAarrival_surfaces}
%\plotone{BBarrival_surfaces}
%\plotone{BCarrival_surfaces}
%\caption{Average reconstructions of each test case assuming time delays and no central image
%using (from \textbf{top} to \textbf{bottom}) the galaxies AA, (AC MISSING), BB, BC.}
%\label{Test reconstructions}
%\end{figure}

@@

\section{Results} %--------------------------------------------------------------

\figref{AAZContrastR1R5_Tm reconstruction} shows a typical reconstruction of a
lens. The far left plot shows the arrival time surface with image marked as
circles and the inferred source position as a diamond. The center plot shows
the radial density profile. The error bars cover the full range of models
generated by \Glass. The true density profile from the mock data is also
plotted for comparison. The vertical lines mark the radial position of the
images. The final plot on the right is of the enclosed mass. As expected the
error bars are smallest in the region of the images where the most information
about the lens is present. The dip in the profile at the end of the profile
is due to the cut off in mass in the lensing map. This is of little importance,
though, as there is no lensing information there.

\begin{figure}
\plotone{AAZContrastR1R5_Tm.pdf}
\caption{A typical reconstructed lens. 
\textbf{(Left)}
The arrival time surface. In this case, there are two sources at different
redshifts with galaxy AA. The next three panels show the radial density,
average enclosed density, and enclosed mass profiles, respectively.  The grey
curve is from the galaxy and the vertical lines show the positions of the
images for the two sources.}
\label{AAZContrastR1R5_Tm reconstruction}
\end{figure}

\begin{figure}
\plotone{AAresults.pdf}
\end{figure}

%\subsection{Model quality}
We estimate the quality of a model $\M_i$ by comparing the recovered
density profile $\rho_\M(r)$ against the profile of the mock galaxy $\rho_G(r)$.
In particular, the plots show the RMS quantity
%
\begin{equation}
  \chi_i = 100 \times \sqrt{\frac{\int_r (\rho_{\M_i}(r) - \rho_G(r))^2}{\int_r \rho_G(r)^2}}
  %\chi_i = \frac{\sum_r (\rho(r)_{\M_i} - \rho(r)_G)^2}{\sum_r \rho(r)_G^2}
\end{equation}

\subsection{Using principle component analysis to find new degeneracies}

@@

\subsection{Aperture}

\begin{figure}
\plotone{sigma_beta.pdf}
\caption{}
\end{figure}

>>>>

\documentclass[onecolumn,galley]{mn2e}
%\documentclass[twocolumn,galley]{mn2e}
%\documentclass[onecolumn,galley,draft]{mn2e}
%\usepackage{myaasmacros}
\usepackage{mathrsfs}
\usepackage{amsmath}
\usepackage{graphicx}

@@

A typical lens, where only the measured observables are the image positions,
can been used to estimate the total mass of a galaxy including parts of the
dark matter halo. The enclosed mass inside the Einstein radius is simple to
calculate and quite robust given the observed image positions. The exact mass
distribution is more difficult to determine, however, as there are typically
not enough constraints on the mass profile. The known degeneracies have been
discussed at length in the literature. At the very least, one would like to
have a measure of the enclosed mass at two distinct radii to be able
to properly distinguish between analytic mass models. 
%This would break the steepness degeneracy, also known as the mass sheet degeneracy.

Lensing is not the only technique that can measure enclosed mass. The enclosed
mass can also be estimated from stellar velocity dispersions. If the radius
from this measurement is sufficiently different from the Einstein radius, then
combining this measurement with lensing provides the necessary constraint.
Another solution is to find a galaxy that is lensing two sources. The images
from each source provide an enclosed mass. The extent to which the radii
differ is dependent upon the redshifts of the two sources: the larger the
redshift difference the larger the radial separation.

Lensing is known to be sensitive to cosmology and, in principle, can be used to
estimate such quantities as the Hubble constant $H_0$ when the lens has
measurable time delays. However, due to strong degeneracies such as the
steepness degeneracy there is often little one can learn from a single lens. 
In this case, one is free to change the mass and $H_0$ while keeping
all observables fixed. A single lens can say almost nothing about the actual
value of $H_0$. However, it has been shown that combining modeling results
of several strong lenses with time delays can significantly reduce the allowed
values and provides a measure to within 10 percent \cite{}.

If one assumes a Hubble constant $H_0$ and time delays have been observed for a
lens this will break the steepness degeneracy but will not help in
constraining the mass profile at two radii.  One can choose to postpone this
problem and simply fit models to the given data.  The earliest examples were
singular isothermal sphere (SIS) or elliptical (SIE) models but have since
evolved to multi-component models include separate models for the stars and
dark matter. Other methods that do not ignore this problem use genetic
algorithms or linear programming to explore the large space of solutions.

Despite such difficulties lensing is a direct probe of the gravitating mass in
a halo and there are a number of open problems in galaxy formation that lensing
can help address. For instance, the debate remains as to what form the inner
slope of the density profile takes. Numerical simulations of dark matter
suggest a cusp, while observations from lensing and stellar dynamics suggest
cores. This may, however, be only a matter of scale, as both theory and
observations agree that clusters have cuspy profiles.

@@

\Glass\ is an evolution of the concepts employed by the free form modeling tool
\PixeLens\ but completely rewritten in Python and C. The key improvements are:
\begin{enumerate}
  \item A modular framework allows new priors to be added and modified easily.
  \item The basis functions approximating a model can be changed. 
  \item Non-linear constraints can be imposed in an automated post-processing step. 
  \item The central region can be have a higher resolution to capture steep models. 
  \item Stellar density can be used as an additional constraint.  
  \item Point or extended mass objects can be placed in the field.
  \item Additional levels of pixel refinement.
\end{enumerate}
At the heart of \Glass\ lies a new algorithm for sampling the high dimensional
linear space that represents the modeling solution space. This algorithm was
described and tested in \cite{}. \Glass\ is also multi-threaded allowing it to
run efficiently on many-cored machines.  The software is freely available for
download. One interesting aspect is that the input files are themselves Python
programs. This allows a large amount of sophistication in setting up a lens at
runtime and also allows \Glass\ to be used as an external library from another
user written program.

@@

For this paper we will restrict ourselves to using the pixelated basis set that
has been employed in previous work and is implemented in \PixeLens. Here we
will briefly review the main ideas. The algorithm for generating models in
\Glass\ samples a convex polytope in a high dimensional space whose interior
points are solutions to the lensing equation and satisfy other physically
motivated linear priors (the sampling algorithm in \Glass\ is not the same as
employed in \PixeLens).  We therefore formulate all of our equations as
equations linear in the unknowns. We describe the density distribution $\kappa$
as a set of discrete grid cells or pixels $\kappa_i$ and rewrite the potential
(\eqnref{lensing potential}) as
%
\begin{equation}
  \psi(\vec\theta) = \sum_n \kappa_n Q_n(\vec\theta)
  \label{discrete potential}
\end{equation}
%
where the sum runs over all the pixels and $Q_n$ is the integral of the logarithm
over pixel $n$. The exact form for $Q$ is described in \appref{Q derivation}.
We can find the discretized lens equation by simply taking the gradient of the
above equations.

The pixels only cover a finite circular area with physical radius $\Rmap$ and
pixel radius $\Rpix$ centered on the lensing galaxy. To account for any global
shearing outside this region from, e.g., a neighboring galaxy, we also add to
\eqnref{discrete potential} two shearing terms
%
\begin{equation}
\gamma_1(\theta_x^2 - \theta_y^2) + 2\gamma_2\theta_x\theta_y\quad.
\end{equation}
%
We can continue adding terms to account for assumed potentials or potentials
induced from the presence of other galaxy in the field. If the stellar density
has been estimated we can use this as a lower bound where the stellar potential
is a known constant of the form \eqnref{discrete potential}.
%
%\begin{equation}
  %\psi^*(\vec\theta) = \sum_n \kappa^*_n Q_n(\vec\theta)\quad.
%\end{equation}
%

Unfortunately, the lens equation and the arrival times alone are not enough to form a
closed volume in the solution space. We have not imposed any strong constraints
on the density even so much as to ensure that it is non-negative everywhere. We
must therefore provide additonal linear constraints so that we only sample
physical models. The explicit implementation for these priors has been
explained in \cite{}, be can be summarized as
\begin{enumerate}
\item The density must be non-negative everywhere.
\item The density profile must have a slope everywhere $\le 0$. This prevents hollow rings.
\item The local gradient everywhere must point within $45^{\circ}$ of the center.
\item Density variations must be smooth.
\item Image parity is enforced.
\item The density is radially symmetric. (Optional)
\end{enumerate}

@@

\subsection{Raytracing}
\label{Raytracing}
\Glass\ can also determine the position of images and time delays from 
particle-based simulation output given a source position $\vec\beta$. This is
used to generate the lens configurations used in the parameter study.  The
particles are first projected onto a very high resolution grid representing the
lens plane. The centers of each of the grid cells are mapped back onto the
source plane using \eqnref{lensing equation}. If the location on the source
plane is within a user specified $\eps_\mathrm{accept}$ of $\vec\beta$ then the
point on the image plane is accepted and further refined using a root finding
algorithm until the distance to $\vec\beta$ is nearly zero. If multiple points
converge to an $\eps_\mathrm{root}$ of each other then only one point is taken.
Care must be taken that the grid resolution is high enough that the resulting
image position error is below the equivalent observational error. Time delays
are then calculated in order from the arrival time at each image (\eqnref{tau}).

@@

The four mock galaxies we consider have been designed to test our recovery
procedure. They are two component models where the dark matter and stellar
profiles are allowed to be steep and shallow.  The enclosed mass in all cases
is fixed at $M(a_\star)= 1.8\e{10}$ at the scale radius $a_\star=2$ kpc. These
values were chosen to closely resemble B1115. We therefore place the galaxy at
a redshift of $z_L = 0.31$ for lensing.  Throughout, we assume a cosmology
where $H_0^{-1}=13.7$ Gyr, $\Omega_M=0.28$, and $\Omega_\Lambda=0.72$. The
critical density is $\kappa_\mathrm{crit}\sim 1.8\e{9}$\Msun/kpc$^2$.

The galaxies were
first generated as three dimensional particle distributions with the
tool DEHNEN-TOOL. Each component follows the profile
\begin{equation}
\rho(r) = \frac{M}{4\pi a^3}(3-\gamma){(r/a)^{-\gamma}(1 + r/a)^{\gamma-4}}
\label{Dehnen profile}
\end{equation}
where $\gamma$ is the profile index and $a$ is the scale radius.  In the
case $\gamma=1$ this is the Hernquist profile.  The four combinations of
profile indices are shown in \tabref{Lens profile params}.  Note that two of
the galaxies have $\gamma_\mathrm{DM}=1$. While we know from simulations that a
more accurate approximation would be an NFW or Einasto profile we are not
probing the outer regions of the halo where the difference would be most
extreme.  The Hernquist profile is easier to generate as it has finite mass.

\begin{table}
\begin{tabular}{cllllllll}
Galaxy & $\gamma_\star$ & $M_\star$ & $\gamma_\mathrm{DM}$ & $M_\mathrm{DM}$ & $\Rmap$ & Notes\\
\hline
AA & 1 & 4 & 0.05 & $11^{2.95}$ & 50 kpc & \\
AC & 1 & 4 & 1 & $11^2$ & 50 kpc & \\
BB & 1.5 & $2^{1.5}$ & 0.16 & $11^{2.84}$ & 50 kpc & \\
BC & 1.5 & $2^{1.5}$ & 1 & $11^2$ & 10 kpc & 
\end{tabular}
\caption{Profile parameters for the four mock galaxies. The resulting profiles only roughly follow
\eqnref{Dehnen profile} because the galaxies are triaxial. Masses are in units of $1.8\e{10}\Msun$. The scale lengths for
all lenses are $(a_\star,a_\mathrm{DM})=(2,20)$ kpc and by definition
$M_\star(a_\star) = M_\mathrm{DM}(a_\star) = 1$.}
\label{Lens profile params}
\end{table}

@@

\begin{enumerate}
\item One double and one extended double.
\item One quad and one extended quad.
\item Three 2-source quads with varying redshift contrast.
\end{enumerate}

The extended configurations use extra sources to generate extra images that
simulate an arc. \figref{config ex.} shows the configuration for the extended
quad.

Each of these configurations were modeled with and without time delays and with
and without a central image. We assumed for all our tests that the lensing mass
was radially symmetric. By construction, this is known to be true and this is
most often the case with real galaxies, unless there is an obvious observed
asymmetry. The central pixel was refined into a further nine pixels to capture
any steep rise in the profile. Two of the four mock galaxies have a steeply rising
inner profile.

\figref{reconstruction} shows a typical reconstruction of a
lens. The far left plot shows the ensemble average arrival time surface with
image marked as circles and the inferred source position as a diamond. The
center plot shows the radial density profile. The error bars cover the full
range of models generated by \Glass. The true density profile from the mock
data is also plotted for comparison. The vertical lines mark the radial
position of the images. The final plot on the right is of the enclosed mass. As
expected the error bars are smallest in the region of the images where the most
information about the lens is present. The dip in the profile at the end of the
profile is due to the cut off in mass in the lensing map. This is of little
importance, though, as there is no lensing information there.

\begin{figure}
%\plotone{AAZContrastR1R5_Tm.pdf}
\plotone{BCQuadR1a_TmS.pdf}
\caption{A typical reconstructed lens. Here we present a single quad lens from 
the BC mock galaxy.
\textbf{(Left)}
The arrival time surface. 
\textbf{(Middle)}
The surface density. The magenta curve represents the dark matter component,
the yellow curve the stellar component, and the blue curve is the sum of the two.
The black curve comes from the original mass model used to create the lens.
The green vertical lines mark the radial positions of the images. The higher
resolution feature of \Glass\ has been used on the central pixel allowing the
steep profile to be captured.
\textbf{(Right)}
The cumulative mass.}
\label{reconstruction}
\end{figure}

The main results from modeling these different configuration are shown black in
\figref{Test reconstructions}. Each subplot corresponds to a different galaxy and
the vertical axis shows the range of quality.  The quality of a
model $\M_i$ by comparing the recovered density profile $\rho_\M(r)$ against
the profile of the mock galaxy $\rho_G(r)$.  In particular, the plots show the
RMS quantity
%
\begin{equation}
  \chi_i = 100 \times \sqrt{\frac{\int_r (\rho_{\M_i}(r) - \rho_G(r))^2}{\int_r \rho_G(r)^2}}
  %\chi_i = \frac{\sum_r (\rho(r)_{\M_i} - \rho(r)_G)^2}{\sum_r \rho(r)_G^2}
\end{equation}
%
\begin{figure}
%\plotone{AAarrival_surfaces}
%\plotone{BBarrival_surfaces}
\plotone{BCarrival_surfaces}
\caption{The lens configurations for the six test cases using the BC mock galaxy. Here,
the central image is shown, although not all tests include it. The central image belongs
to only one set of images to avoid overconstraining the models. Similar colors group
images that share a common source. In the case of the extended image systems the source
is at the same redshift, while the redshift is varied between the systems in the 
ZConstrast cases. Grey circles are a visual aid to help determine radial separation
between images. The axes are measure in arcseconds.}
\label{Test reconstructions}
\end{figure}

The morphological complexity increases from left to right within each plot. As
a result, there is a general trend for the reconstruction quality to increase
(and for $\chi$ to decrease). By adding more measurable information to each
configuration the quality can also be affected. When both time delays and a
central image are present the quality is highest. A double is known to provide
very little constraint on the mass distribution. This is particular evident in
galaxies AC and BC where the mass profile is steepest and the reconstruction of
the double is poorest. However, the addition of an arc is sufficient to correct
this.

\subsection{Stellar mass}

The previous tests have been conducted to show that \Glass\ performs as expected.
Here, we present a novel constraint that can significantly improve the models. 
The stellar mass distribution is a lower bound on the total mass and in the
central region of a galaxy is also the dominant component. It can therefore be
used to constrain the innermost profile. We took the stellar mass directly from
the generated galaxies and projected the particles onto the pixels. \Glass\
also offers an option to interpolate any map of stellar mass (e.g., from an
observation) onto the pixels. The linear constraint is added to \Glass\ by
writing $\kappa_n = \kappa_{dm,n} + \kappa_{s,n}$ as the sum of the
dark matter and stellar mass components in the potential (\eqnref{discrete
potential}). Since each $\kappa_{s,n}$ is just a constant we do not add new,
separate equations for each pixel.

With the stellar mass lower bound, the improvement of the reconstruction
quality shown in \figref{Test reconstructions} is quite dramatic for the
steepest mock galaxies (AC and BC). This is because these models are dominated
by stars in the inner region. The other two galaxies are unaffected because the
models were already well modeled by the dark matter alone.

\subsection{Velocity anisotropy}

In addition to the lens model aspects, \Glass\ can also run post processing
routines to analyze each model as it is produced. We have developed a number of
routines for fitting analytic models to the lensing mass profiles. One in
particular deprojects the 2d profile assuming a Hernquist profile for the
light. By fixing the velocity anisotropy $\beta$ we can determine the velocity
dispersion of the model. Of course, the true velocity dispersion is known for
the mock galaxies and we can compare our method to those measurements.  In
\figref{sigma-beta} we plot the recovered velocity dispersion for $\beta=0$ and $\beta=1$
over a range of aperture sizes for the BC Quad with time delays and stellar
mass. The stellar half mass radius is plotted in yellow and the Einstein radius
in black. For this configuration the two radii are well separated. This plot
demonstrates that the velocity anisotropy can be inferred by combining lens
modeling and independent velocity dispersion measurements. The lens breaks
the anisotropy degeneracy at a given aperture.

\begin{figure}
\plotone{BCQuadR1a_TmS-sb.pdf}
\caption{Estimated velocity dispersion as a function of the aperture size. The
single quad lens model for the BC mock galaxy was deprojected and the mass
profile fit assuming a Hernquist profile for the light. The top curve (blue)
assumes a velocity anisotropy $\beta=1$, while the lower curve (green)
assumes $\beta=0$. Given an independent estimate of the velocity dispersion,
lensing can be used to place constraints on the velocity anisotropy.}
\label{sigma-beta}
\end{figure}

%\subsection{Velocity dispersions}
%
%\begin{itemize}
%\item Can they predict radial profiles?
%\item Can we constrain lensing models from predicted velocity dispersions?
%\item Use a constructed spherical halo G2 following a $\rho \propto r^{-\gamma}$ profile with stellar halo same as G1.
%\item Vary $z$ of the halo, possibly orientation.
%\item Should be able to recover $\gamma$ very well.
%\item Use G1. Show problems with recovering $\gamma$.
%\end{itemize}

@@

@@

%\section{Results} %--------------------------------------------------------------

%\begin{figure}
%\plottwo{AAchi2_profile.pdf}{BBchi2_profile.pdf}
%\plottwo{ACchi2_profile.pdf}{BCchi2_profile.pdf}
%\end{figure}

%\subsection{Model quality}

%\subsection{Shape fitting}

%\subsection{Using principle component analysis to find new degeneracies}

@@

%\subsection{Aperture}

%\begin{figure}
%\plotone{sigma_beta.pdf}
%\caption{}
%\end{figure}
